\documentclass[11pt]{article}
\input{headers02}

\usepackage{fancyhdr}   
\pagestyle{fancy}      
\lhead{}               
\rhead{Harris Christiansen (christih@purdue.edu)} %%% <-- YOUR NAME HERE

\usepackage[strict]{changepage}  
\newcommand{\nextoddpage}{\checkoddpage\ifoddpage{\ \newpage\ \newpage}\else{\ \newpage}\fi}  


\begin{document}

\title{Homework 2}

\date{}

\maketitle 

\thispagestyle{fancy}  
\pagestyle{fancy}      




\begin{enumerate}

%%% Problem 1 
\item {\bfseries Defining Multiplication over $\bbZ_{27}^*$.} 
  In the class, we had considered the group $(\bbZ_{26},+)$ to construct a one-time pad for one alphabet messages. 
  A few students were interested to define a group with 26 elements using a ``multiplication''-like operation. 
  This problem will assist you to define the $(\bbZ_{27}^*,\times)$ group. 
  
  Interpret $\bbZ_{27}^*$ as the set of all triplets $(a_0,a_1,a_2)$ such that $a_0,a_1,a_2 \in \bbZ_3$ and at least one of them is non-zero (you can think of the triplets as the ternary representation of the elements in $\bbZ_{27}^*$). 
  We shall equivalently interpret the element $(a_0,a_1,a_2)$ as the polynomial $a_0 + a_1X + a_2X^2$. 
  So, every element in $\bbZ_{27}^*$ has an associated non-zero polynomial of degree at most 2, and every non-zero polynomial of degree at most 2 has an element in $\bbZ_{27}^*$ associated with it. 
  
  The multiplication ($\times$ operator) of the element $(a_0,a_1,a_2)$ with the element $(b_0,b_1,b_2)$ is defined as the element corresponding to the polynomial
    $$(a_0 + a_1X + a_2X^2) \times (b_0 + b_1X + b_2X^2) \mod X^3 + 2X + 2$$
  According to this definition of the $\times$ operator, find
  \begin{itemize}
  \item (10 points) $(1,2,1) \times (2,2,1) $
  \item (15 points) the inverse of $(1,2,1)$.
  \end{itemize}
  {\bfseries Solution.} 
  \begin{itemize} 
  \item $(1,2,1) \times (2,2,1) $
   	\[(a_0 + a_1X + a_2X^2) \times (b_0 + b_1X + b_2X^2) \mod X^3 + 2X + 22\]
 	\[(1 + 2X + X^2) \times (2 + 2X + X^2) \mod X^3 + 2X + 2\]
 	\[2 + 4X +2X^2) + (2X + 4X^2 + 2X^3) + (X^2 + 2X^3 + X^4 \mod X^3 + 2X + 2\]
 	\[2 + 0X + X^2 + X^3 + X^4 \mod X^3 + 2X + 2\]
 	\[2 + 0X + X^2 - (2X+2) - (2X^2+2X) \mod X^3 + 2X + 2\]
 	\[0 + 2X + 2X^2 \mod X^3 + 2X + 2\]
 	\[(0, 2, 2)\]
  \item the inverse of $(1,2,1)$. 
 	\[(1 + 2X + X^2) \times (b_0 + b_1X + b_2X^2) \mod X^3 + 2X + 2\]
 	\[(b_0 + b_1X + b_2X^2) + (2b_0X + 2b_1X^2 + 2b_2X^3) + (b_0X^2 + b_1X^3 + b_2X^4) \mod X^3 + 2X + 2\]
 	\[b_0 + (b_1+2b_0)X + (b_2+2b_1+b_0)X^2 + (2b_2+b_1)X^3 + b_2X^4 \mod X^3 + 2X + 2\]
 	\[b_0 + (b_1+2b_0)X + (b_2+2b_1+b_0)X^2 - (2b_2+b_1)(2X+2) - b_2(2X^2+2X) \mod X^3 + 2X + 2\]
 	\[b_0 + (b_1+2b_0)X + (b_2+2b_1+b_0)X^2 - (b_2+2b_1) - (b_2+2b_1)X - (2b_2)X - (2b_2)X^2 \mod X^3 + 2X + 2\]
 	\[(b_0+b_1+2b_2) + (2b_0+2b_1)X + (2b_2+2b_1+b_0)X^2 \mod X^3 + 2X + 2\]
 	\[(0, 0, 0) \textrm{ when } b_0 = 2, b_1 = 2, b_2 = 1\]
 	\[(1, 2, 2)\]
  \end{itemize}

\nextoddpage 
%%% Problem 2 
\item {\bfseries One-time Pad for 3-Alphabet Words.} 
  We interpret $a,b,\dotsc,z$ as $0,1,\dotsc,25$. 
  We will work over the group $(\bbZ^3_{26},+)$, where $+$ is coordinate-wise integer-sum $\mod 26$. 
  For example, $abx + acd = ada$. 
  
  Now, consider the one-time pad encryption scheme over the group $(\bbZ^3_{26},+)$. 
  \begin{itemize}
  \item (12.5 points) What is the probability that the encryption of the message $cat$ is the cipher text $cat$?
  $$P(cipher="cat" given message="cat") = P(secretkey="aaa") = (1/26)^3 = 0.0000569$$
  \item (12.5 points) What is the probability that the encryption of the message $cat$ is the cipher text $dog$? 
  $$P(cipher="dog" given message="cat") = P(secretkey="bon") = (1/26)^3 = 0.0000569$$
  \end{itemize}  
  
  
\nextoddpage 
%%% Problem 3 
\item {\bfseries Left Identity and Left Inverse.} 
  Recall that when we defined a group $(G,\circ)$, we stated that there exists an element $e$ such that for all $x\in G$ we have $x\circ e=x$. 
  Note that $e$ is ``applied on $x$ from the right.'' 
  
  Similarly, for every $x\in G$, we are guaranteed that there exists $\inv(x)\in G$ such that $x\circ\inv(x)=e$. 
  Note that $\inv(x)$ is again ``applied to $x$ from the right.'' 
  
  Intuitively, we shall explore the following questions: (a) Is there an ``identity from the left?,'' and (b) Is there an ``inverse from the left?'' 
  
  We shall formalize and prove these results in this question. 
  \begin{itemize}
  \item (10 points) Prove that $e\circ x = x$, for all $x\in G$. 
  \item (10 points) Prove that if there exists an element $\alpha\in G$ such that for all $x\in G$ we have $\alpha\circ x=x$, then $\alpha = e$. 
  \end{itemize}
  Note that these two steps prove that the ``left identity'' is identical to the right identity $e$. 
  
  
  \begin{itemize}
  \item (10 points) Prove that $\inv(x)\circ x = e$. 
  \item (10 points) Prove that if there exists an element $\alpha\in G$ and $x\in G$ such that $\alpha\circ x=e$, then $\alpha=\inv(x)$. 
  \end{itemize}
  Note that these two steps prove that the ``left inverse of $x$'' is identical to the left inverse $\inv(x)$. 
  
  Finally, we can prove the following result crucial to the proof of security of one-time pad over the group $(G,\circ)$. 
  \begin{itemize}
  \item (10 points) Suppose $m\in G $ is a message and $c\in G$ is a cipher text. 
    Prove that there exists a unique $\sk\in G$ such that $m\circ \sk = c$. 
  \end{itemize}
  
  {\bfseries Solution.} 
  \begin{itemize} 
  \item {\bfseries Prove that $e\circ x = x$, for all $x\in G$.} \\
  Proof by contradiction. Suppose there exists $x$ such that $e \circ x \neq x$ \\
  By performing the $\circ \inv(x)$ function on both sides, we get $e \circ (x \circ inv(x)) \neq x \circ inv(x) \equiv e \circ e \neq e \equiv e \neq e $ \\
  Proof by contradiction, $e\circ x = x$
  
  \item {\bfseries Prove that if there exists an element $\alpha\in G$ such that for all $x\in G$ we have $\alpha\circ x=x$, then $\alpha = e$. } \\
  Suppose there exists $\alpha$ such that $\alpha \circ x = x$ \\
  Let $x = e$, such that $\alpha \circ e = e$ \
  Given $\alpha \circ e = \alpha$, we can conclude $\alpha = e$
  
  \item {\bfseries Prove that $\inv(x)\circ x = e$. } \\
  Given that $x \circ \inv(x) = e$ and  $x \circ e = x$ \\
  Then $\inv(x) = \inv(x) \circ e = \inv(x) \circ (x \circ \inv(x)) = (\inv(x) \circ x) \circ \inv(x) $ \\
  It follows that $e = \inv(x) \circ \inv(\inv(x)) = (\inv(x) \circ x) \circ \inv(x) \circ \inv(\inv(x)) = (\inv(x) \circ x) \circ e = \inv(x) \circ x$ \\
  $\inv(x) \circ x = e$
  
  \item {\bfseries Prove that if there exists an element $\alpha\in G$ and $x\in G$ such that $\alpha\circ x=e$, then $\alpha=\inv(x)$. } \\
  Suppose $\alpha \circ x = e$ \\
  Then  $\alpha \circ x = e \equiv \alpha \circ x \circ \inv(x) = e \circ \inv(x) \equiv \alpha \circ e = e \circ \inv(x) \equiv \alpha = \inv(x)$
  
  \item {\bfseries Suppose $m\in G $ is a message and $c\in G$ is a cipher text. 
    Prove that there exists a unique $\sk\in G$ such that $m\circ \sk = c$. } \\
  Given $m,c\in G $, suppose $m\circ \sk = c$ \\
  This would imply that $m\circ \sk \circ \inv(m) = c \circ \inv(m) \equiv \sk = c \circ \inv(m)$ \\
  Therefor, there exists a $\sk\in G$ for every $m,c\in G $ where $\sk = c \circ \inv(m)$
  \end{itemize}

\nextoddpage 
%%% Problem 4 
\item {\bfseries One-time Pad with non-uniform secret key.} 
  (25 points) Consider the one-time pad encryption scheme over a group $(G,+)$. 
  Suppose the a priori distribution of messages is the uniform distribution over the set $G$. 
  Suppose the generation algorithm samples the secret-key $\sk$ according to the distribution $\cD$ over the sample space $G$ such that $\cD$ is {\em not} the uniform distribution over $G$. 
  Is this encryption scheme secure? 
  
  (\footnotesize{\em Remark:} 
    To prove that the scheme is secure, provide a proof that the a priori distribution of messages is same as the a posteriori distribution. 
    To prove that the scheme is insecure, provide a proof that the a priori distribution of messages is different from the a posteriori distribution.)
  
  {\bfseries Solution.} 
  \begin{itemize} 
  \item Because the distribution $\cD$ is not uniform, there exists a $\sk_p$ where $\probX{SK = \sk_p} > 1/\abs G$ n
 	Consider a message m ciphered with secret key $\sk_p$, such that $\sk_p = \inv(m) \circ c$. Because distribution $\cD$ is not uniform, it is clear that $\probX{M = m | C = c} > \probX{M = m}$ and thus that this non-uniform one-time pad is {\bfseries NOT} secure.
  \end{itemize}
    
    
    
\nextoddpage 
%%% Problem 5 
\item {\bfseries Designing Encryption Scheme.} 
  We shall work over the field $(\bbZ_{11},+,\times)$. 
  Assume that there are ten people $\{1,2,\dotsc,10\}$. 
  Design a private-key encryption scheme for the following scenario. 
  
  Alice meets the ten people $\{1,2,\dotsc,10\}$ today. 
  She can provide each of them information $\{s_1,s_2,\dotsc,s_{10}\}$. 
  
  Tomorrow, Alice shall encrypt a message $m\in\bbZ_{11}$. 
  The encryption has to ensure that decryption should be possible if and only if two people among $\{1,\dotsc,5\}$ and three people among $\{6,\dotsc,10\}$ get together.
  
  
  \begin{itemize}
  \item (15 points) Provide the $(\gen,\enc,\dec)$ algorithms. 
  \item (15 points) Proof of security of this scheme. 
  \end{itemize}
  
  {\bfseries Solution.} 
  \begin{itemize} 
  \item We will use Shamir's secret sharing to divide the secret encryption key among the two groups of 5 people each. \\
  gen: Generate secret key $\sk$ and use Shamir's secret sharing to divide $\sk$ into ($s_1$ and $s_2$) such that both shares are required. Key $s_1$ will then be divided among group 1 (individuals [1,2,3,4,5]) using Shamir's such that any 2 shares can unlock $s_1$. Key $s_2$ will be divided among group 2 (individuals [6,7,8,9,10]) using Shamir's such that any 3 shares can unlock $s_2$. \\
  enc: Encrypt message m with secret key $\sk$ \\
  dec: Determine $s_1$ using 2 shares from group 1, and $s_2$ using 3 shares from group 2. Use $s_1$ and $s_2$ to determine $\sk$ and use $\sk$ to decrypt cipher c
  \item $\sk$ is needed to decrypt cipher c, and $\sk$ can only be determined by both shares $s_1$ and $s_2$. Because of Shamir's secret sharing scheme, without all shares, the cipher c is still guaranteed to be secure. Even if an attacker obtained ($s_1$ or $s_2$) and (all except 1 share for the other), the cipher would still be secure.
  \end{itemize}
 






\nextoddpage 
%%% Problem 6
\item {\bfseries A property of 2-wise Independence.} 
  Let \cH be a hash function family from the domain \cD to the range \cR. 
  \begin{itemize}
  \item (20 points) Similar to the proof in the lectures for universal hash function family, prove the following. 
    There exists distinct $x_1^*,x_2^*\in\cD$ and $y_1^*,y_2^*\in\cR$ such that 
      $$\probX{h(x^*_1)=y^*_1,h(x^*_2)=y^*_2\colon h\getsr\cH} \geq \frac1{\abs\cR^2}$$
    ({\em Remark:} Note that this result does not depend on whether $\abs\cR < \abs\cD$ or not.) 
  \item (25 points) Now, suppose that $\abs\cR < \abs\cD$. 
    Suppose that for all distinct $x_1,x_2\in\cD$ the following holds.  
    $$\probX{h(x_1)=h(x_2)\colon h\getsr\cH} < \frac1{\abs\cR}$$
    Prove that there exists distinct $x_1^*,x_2^*\in\cD$ and $y_1^*,y_2^*\in\cR$ such that 
      $$\probX{h(x^*_1)=y^*_1,h(x^*_2)=y^*_2\colon h\getsr\cH} > \frac1{\abs\cR^2}$$
  \end{itemize}
  This result proves that if a universal hash-function family has collision probability $<\frac1{\abs\cR}$ then it is not pairwise independent. 
  
  {\bfseries Solution.} 
  \begin{itemize} 
  \item Asdf
  \end{itemize}



\nextoddpage 
%%% Problem 7 
\item {\bfseries Extra Credit.} 
  Suppose $\cD=\zo^n$ and $\cR=\zo^{n-1}$. 
  Construct a hash function family such that for all distinct $x_1,x_2\in\cD$ we have 
  $$\probX{h(x_1)=h(x_2)\colon h\getsr\cH} = \frac1M \cdot\left(\frac{N-M}{N-1}\right),$$
  where $N=2^n$ and $M=2^{n-1}$.  
  Try to construct a hash function family such that each hash function can be efficiently evaluated. 
  
  {\bfseries Solution.} 
  \begin{itemize} 
  \item Asdf
  \end{itemize}
 



\end{enumerate}









\end{document}
